Fail Faster

### 2025-03-12 paper/paper.tex
reframe

@@

% \subsubsection{Function call overhead}
\subsubsection{Boxed RNG}

\jwc{
  \begin{itemize}
    \item Because the RNG sits at the heart of the generation hot path, RNG speed matters enormously.
    \item To illustrate this, we demonstrate a particular inefficiency of
    OCaml's BQ, resolve it in a later section, and then show how much you can
    bug-finding performance just by speeding up and RNG.
    \item We also demonstrate how using an inequivalent RNG
    \item Scalacheck uses a faster RNG called ``xoroshiro128++'' \cn{}.
    % https://lemire.me/blog/2019/03/19/the-fastest-conventional-random-number-generator-that-can-pass-big-crush/
    \item One could go even faster, using \href{https://lemire.me/blog/2019/03/19/the-fastest-conventional-random-number-generator-that-can-pass-big-crush/}{even faster RNG} with less guarantees.
  \end{itemize}
}

>>>>

\jwc{``Property based testing is a race against time...''}

@@

% \subsubsection{Function call overhead}
\subsubsection{Choice of RNG}

\jwc{
  \begin{itemize}
    \item Because the RNG sits at the heart of the generation hot path, RNG
    speed matters enormously. Which RNG you pick matters...

    \item Different PBT libraries use different RNGs --- QuickCheck and \bq use
    splittable_random, Scalacheck uses \href{https://burtleburtle.net/bob/rand/smallprng.html}{this one}.  These
    are reasonably performant RNGs, but faster ones exist. Because this is the
    core of the hot path of the generator, speeding up sampling just a little can
    can dramatically speed up generation time.
    \item Significantly faster RNGs that still pass pRNG benchmarks like BigCrush exist (like \href{https://github.com/lemire/testingRNG/blob/master/source/lehmer64.h}{this one}), and using them can 
    speed up generation enormously.

    \item However, showing this
    is tricky, because different RNGs have different sampling orders, but our
    eval is made much stronger by the fact that all of our generators are functionally equivalent.

    \item In this paper demonstrate this fact by noticing a ``natural experiment'': OCaml's splittable random library is
    slow in a way that can be improved \emph{without} changing the extensional behavior. By resolving this issue, we can demonstrate
    just how much you can improve bug-finding performance simply by speeding up the RNG.

    % To illustrate this, we demonstrate a particular inefficiency of
    % OCaml's BQ, resolve it in a later section, and then show how much you can
    % bug-finding performance just by speeding up and RNG.
  \end{itemize}
}
